Object-based Auditory Scenes Similarity Retrieval and Classification With Wavelet Scattering

### 2016-07-12 paper/structureScene.tex
Edit conclusion

Representing a scene using a reduced set of representatives, with adapted similarity strategies allows us to improve ASSR performance compared to the BOF approaches based on GMMs. These results advocate for a hierarchical model of the scene, where short-time structure -- \ie below a second -- are represented using a convolutional network such as the scattering transform, whereas larger time scales -- \ie over a second -- are modeled as adaptive aggregates.

Within a supervised setting of acoustic scene classification (ASC), we have shown the comparative benefits of log-scattering features over MFCCs, of majority voting at a mid-level time scale of $T=372\,\mathrm{ms}$ over prediction at a high-level time scale of $T=24\,\mathrm{s}$, and of an adapted Gaussian kernel over the linear kernel in support vector machine (SVM) classification.
%, identified in the time domain in the unsupervised setting and in the features domain in the supervised case, provided that the dimensionality is sufficiently high. \ja{I'm not sure what this last part means.}

>>>>

Representing a scene using a reduced set of representatives, with adapted similarity strategies allows us to improve ASSR performance compared to the BOF approaches based on GMMs. These results advocate for a hierarchical model of the scene, where short-time structure -- \ie below a second -- is represented using a convolutional network such as the scattering transform, while larger time scales -- \ie over a second -- are modeled as adaptive aggregates.

Within a supervised setting of acoustic scene classification (ASC), we have shown the comparative benefits of log-scattering features over MFCCs, of majority voting at a mid-level time scale of $T=372\,\mathrm{ms}$ over prediction at a high-level time scale of $T=24\,\mathrm{s}$, and of an adapted Gaussian kernel over the linear kernel in support vector machine classification.
%, identified in the time domain in the unsupervised setting and in the features domain in the supervised case, provided that the dimensionality is sufficiently high. \ja{I'm not sure what this last part means.}
